Discrete Ordinates

### 2017-06-03 docprep/chapresults.tex
Updated the header
Minor fixes and added some figs

%%
%% This is file `chapmin.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% ths.dtx  (with options: `chapmin')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from chapmin.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file ths.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)

@@

@@

>>>>

%%
%% Edward T. Norris
%% Discrete Ordinates Computed Tomography Organ Dose Simulator (DOCTORS)
%% 
%% === Results ===
%%

@@

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=3.75in]{figs/bench_cone1_centerdiff3}
  \end{center}
  \caption{The 19 group center flux comparison}
\label{fig:bench_cone1_centerdiff3}
\end{figure}

A plot is below.

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=3.75in]{figs/bench_cone1_centerdiff47}
  \end{center}
  \caption{The 47 group center flux comparison}
\label{fig:bench_cone1_centerdiff47}
\end{figure}

The analytical point is computed as
\begin{equation}
\frac{d\varphi}{dE} = \frac{e^{-(\mu^g_a x_a + \mu^g_w x_w)}}{4\pi G (x_a + x_w)^2 (\Delta E)^g}
\end{equation}
where $\mu_a^g$ and $\mu_w^g$ are the attenuation coefficients for air and water repectively for the $g$ group, $x_a$ and $x_w$ are the pathlength through air and water respectively, and $\Delta E$ is the width of the $g$ group in MeV.

@@

\section{GPU Acceleration}

it's faster!
